---
title: "Lab 6 – Finding and assessing community structure"
author: "Boschetto Ilaria, Volpi Davide"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    number_sections: true
fontsize: 11pt
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.width = 7, fig.height = 5)
library(igraph)
library(igraphdata)
library(clustAnalytics)
library(tidyverse)
library(conflicted)
set.seed(12345)
conflict_prefer("union", "base")
conflict_prefer("intersect", "base")
conflict_prefer("setdiff", "base")
```
**Task 1:** Write an R function that, given two different clusterings of the same network, outputs a table of the Jaccard index between each of their clusters.

The Jaccard index between two sets A and B is defined as: $J(A,B) = \frac{|A \cap B|}{|A \cup B|}$

```{r}
# Function to compute Jaccard similarity matrix between two clusterings
# memb1: membership vector for first clustering
# memb2: membership vector for second clustering
# Returns: matrix where element (i,j) is Jaccard index between cluster i of 
#          clustering 1 and cluster j of clustering 2
jaccard_sim <- function(memb1, memb2) {
  if(length(memb1) != length(memb2)) {
    stop("Membership vectors must have the same length")
  }
  
  # Get unique cluster labels for both clusterings
  unique1 <- sort(unique(memb1))
  unique2 <- sort(unique(memb2))
  
  # Initialize Jaccard similarity matrix
  JS <- matrix(0, nrow = length(unique1), ncol = length(unique2),
               dimnames = list(paste0("C1.", unique1), paste0("C2.", unique2)))
  
  # Compute Jaccard index for each pair of clusters
  for(i in seq_along(unique1)) {
    # Get indices of nodes in cluster i of clustering 1
    A_idx <- which(memb1 == unique1[i])
    
    for(j in seq_along(unique2)) {
      # Get indices of nodes in cluster j of clustering 2
      B_idx <- which(memb2 == unique2[j])
      
      # Compute intersection and union
      inter <- length(intersect(A_idx, B_idx))
      uni <- length(union(A_idx, B_idx))
      
      # Jaccard index: |A ∩ B| / |A ∪ B|
      JS[i, j] <- if(uni == 0) 0 else inter/uni
    }
  }
  return(JS)
}
```



**Task 2 :** Write a function that for each cluster of labeling 1, identifies which is the cluster of labeling 2 that is most similar according to the Jaccard index.

```{r}
# Function to match clusters based on maximum Jaccard similarity
# JS: Jaccard similarity matrix from jaccard_sim()
# name1, name2: names for the two clusterings (for output labeling)
# Returns: list with pairs, column indices, and Jaccard values of best matches
match_clusters <- function(JS, name1 = "L1", name2 = "L2") {
  # For each row (cluster in clustering 1), find column with maximum Jaccard
  best_cols <- apply(JS, 1, function(r) { 
    if(all(is.nan(r))) NA else which.max(r) 
  })
  
  # Create pair labels: (C1.i, C2.j) where j is best match for i
  pairs <- mapply(function(r, c) {
    paste0("(", name1, ".", rownames(JS)[r], ",", 
           name2, ".", colnames(JS)[c], ")")
  }, r = seq_len(nrow(JS)), c = best_cols, SIMPLIFY = TRUE)
  
  # Extract Jaccard values for best matches
  values <- mapply(function(r, c) JS[r, c], 
                   r = seq_len(nrow(JS)), c = best_cols)
  names(values) <- pairs
  
  list(pairs = pairs, cols = best_cols, values = values)
}
```

**Task 3:** Write a function that computes the weighted mean of the Jaccard indices, with weights given by the fraction of nodes in each cluster. This represents the global Jaccard similarity between two clusterings.

```{r}
# Function to compute weighted mean of Jaccard similarities
# match_obj: output from match_clusters()
# memb1: membership vector of first clustering (to compute weights)
# Returns: weighted mean where weights are proportional to cluster sizes
Wmean <- function(match_obj, memb1) {
  unique1 <- sort(unique(memb1))
  
  # Compute size of each cluster in clustering 1
  sizes <- sapply(unique1, function(label) sum(memb1 == label))
  
  # Weights are fractions: size_i / total_nodes
  weights <- sizes / sum(sizes)
  
  # Weighted mean of Jaccard values
  sum(weights * unname(match_obj$values))
}
```

**Task 4:** Evaluate the significance of clusterings produced by different community detection methods on four networks using both scoring functions and Jaccard similarity.

## Setup: Algorithms to Evaluate

We evaluate at least: Louvain, Label Propagation, Walktrap, and Edge Betweenness.

```{r}
# List of community detection algorithms to evaluate
alg_list <- list(
  Louvain = function(g) cluster_louvain(g),
  "Label Prop." = function(g) cluster_label_prop(g),
  Walktrap = function(g) cluster_walktrap(g),
  EdgeBetw = function(g) cluster_edge_betweenness(g)
)
```

## Setup: Network Graphs

1. Karate club (known ground truth)
2. Synthetic network: 200 nodes, 800 edges, 4 communities with scale-free distribution
3. ENRON network (converted to undirected simple weighted graph)
4. A network of choice with no known community structure

```{r}
# Network 1: Karate Club (ground truth available)
data(karate, package = "igraphdata")
g_karate <- karate
g_karate <- igraph::upgrade_graph(g_karate)
memb_gt_karate <- V(g_karate)$Faction

# Network 2: Synthetic network with 4 communities
B <- matrix(0.3, 4, 4)  
diag(B) <- 0.7          

g_synth <- barabasi_albert_blocks(
  m = 4,
  p = c(0.25, 0.25, 0.25, 0.25),
  B = B,
  t_max = 200,
  type = "Hajek",
  sample_with_replacement = FALSE
)

memb_gt_synth <- V(g_synth)$label

# Network 3: ENRON network
data(enron, package = "igraphdata")
g_enron <- as.undirected(enron, mode = "collapse")
E(g_enron)$weight <- 1
g_enron <- igraph::simplify(g_enron, remove.multiple = TRUE, remove.loops = TRUE, edge.attr.comb = list(weight='sum'))
g_enron <- igraph::upgrade_graph(g_enron)

# Network 4: Network of choice - Macaque Cortical Network
data(macaque, package = "igraphdata")
g_macaque <- macaque
g_macaque <- as.undirected(g_macaque)
g_macaque <- igraph::simplify(g_macaque)
g_macaque <- igraph::upgrade_graph(g_macaque)


# Store all graphs with their ground truth 
graphs <- list(
  karate = list(g = g_karate, gt = memb_gt_karate, name = "Karate Club"),
  synth  = list(g = g_synth,  gt = memb_gt_synth, name = "Synthetic Network"),
  enron  = list(g = g_enron,  gt = NULL, name = "ENRON Email Network"),
  macaque = list(g = g_macaque, gt = NULL,name = "Macaque Cortical Network")
)
```

## Comprehensive Evaluation Function

**Note from PDF (page 6):** "Beware of random nature of some clustering algorithms (e.g. walktrap); hence... you should at least consider running the evaluation... several times and work with the averages."

This function implements the complete evaluation pipeline:
- Runs each algorithm multiple times (to handle randomness)
- Computes significance scores using clustAnalytics
- Determines reference clustering (ground truth or best-scoring)
- Computes Jaccard similarities (local and global)

```{r}
evaluate_graph <- function(g, gt = NULL, alg_list = alg_list, n_reps = 5) {
  
  cat("\n=== Starting Evaluation ===\n")
  cat("Graph size:", vcount(g), "nodes,", ecount(g), "edges\n")
  
  # Ensure ground truth matches graph size
  if(!is.null(gt) && length(gt) != vcount(g)) {
    warning(paste("Ground truth length", length(gt), 
                  "does not match graph size", vcount(g), 
                  "- ignoring ground truth"))
    gt <- NULL
  }
  
  # STEP 1: Run each algorithm n_reps times (to handle randomness - PDF page 6)
  cat("\nStep 1: Running algorithms", n_reps, "times each...\n")
  alg_results <- list()
  for(alg_name in names(alg_list)) {
    cat("  Running", alg_name, "...")
    membs <- vector("list", n_reps)
    for(r in seq_len(n_reps)) {
      set.seed(1000 + r)
      cl <- tryCatch(alg_list[[alg_name]](g), error = function(e) NULL)
      membs[[r]] <- if(is.null(cl)) NA else membership(cl)
    }
    alg_results[[alg_name]] <- membs
    cat(" done\n")
  }

  # STEP 2: Evaluate significance multiple times and average (PDF page 6)
  # "you should at least consider running the evaluation of significance 
  #  of these clustering algorithms several times and work with the averages"
  cat("\nStep 2: Evaluating significance with scoring functions (", n_reps, "times)...\n")
  
  sig_tabs <- list()
  for(r in seq_len(n_reps)) {
    cat("  Repetition", r, "/", n_reps, "\n")
    
    alg_for_eval <- lapply(names(alg_list), function(a) {
      function(graph) alg_list[[a]](graph)
    })
    names(alg_for_eval) <- names(alg_list)
    
    sig_tab_r <- tryCatch(
      evaluate_significance(g, alg_list = alg_for_eval, gt_clustering = gt),
      error = function(e) {
        warning("evaluate_significance failed: ", e$message)
        NULL
      }
    )
    
    sig_tabs[[r]] <- sig_tab_r
  }
  
  # Compute average significance scores across repetitions
  if(all(sapply(sig_tabs, is.null))) {
    sig_tab_avg <- NULL
    cat("  All significance evaluations failed\n")
  } else {
    # Remove NULL entries
    sig_tabs <- sig_tabs[!sapply(sig_tabs, is.null)]
    
    # Average across repetitions
    alg_names <- rownames(sig_tabs[[1]])
    score_names <- colnames(sig_tabs[[1]])
    
    sig_tab_avg <- matrix(0, nrow = length(alg_names), ncol = length(score_names))
    rownames(sig_tab_avg) <- alg_names
    colnames(sig_tab_avg) <- score_names
    
    for(r in seq_along(sig_tabs)) {
      sig_tab_avg <- sig_tab_avg + sig_tabs[[r]]
    }
    sig_tab_avg <- sig_tab_avg / length(sig_tabs)
    sig_tab_avg <- as.data.frame(sig_tab_avg)
    
    cat("  Averaged scores across", length(sig_tabs), "successful runs\n")
  }

  # STEP 3: Determine reference clustering (PDF page 6)
  # "Take as the reference clustering the ground truth, if it is known; 
  #  or the best ranked clustering... otherwise."
  cat("\nStep 3: Determining reference clustering...\n")
  if(!is.null(gt)) {
    ref_memb <- gt
    ref_name <- "GroundTruth"
    cat("  Using ground truth as reference\n")
  } else if(!is.null(sig_tab_avg) && nrow(sig_tab_avg) > 0) {
    # Find best algorithm based on AVERAGED modularity (high is best)
    cat("  Available columns in sig_tab:", paste(colnames(sig_tab_avg), collapse = ", "), "\n")
    
    if("Modularity" %in% colnames(sig_tab_avg)) {
      best_alg <- rownames(sig_tab_avg)[which.max(sig_tab_avg[, "Modularity"])]
    } else if("modularity" %in% colnames(sig_tab_avg)) {
      best_alg <- rownames(sig_tab_avg)[which.max(sig_tab_avg[, "modularity"])]
    } else {
      # Use first algorithm as fallback
      best_alg <- rownames(sig_tab_avg)[1]
    }
    
    # Verify the algorithm exists in our results
    if(best_alg %in% names(alg_results)) {
      ref_memb <- alg_results[[best_alg]][[1]]
      ref_name <- paste0("BestByAvgScore_", best_alg)
      cat("  Using best scoring algorithm (by average) as reference:", best_alg, "\n")
    } else {
      # Fallback to Louvain
      ref_memb <- alg_results$Louvain[[1]]
      ref_name <- "Louvain_fallback"
      cat("  Best algorithm not found, using Louvain as fallback\n")
    }
  } else {
    # Fallback to Louvain
    ref_memb <- alg_results$Louvain[[1]]
    ref_name <- "Louvain_fallback"
    cat("  No significance table available, using Louvain as fallback\n")
  }

  # STEP 4: Calculate Jaccard similarities (local and global)
  # This implements Tasks 1, 2, and 3 from the PDF
  cat("\nStep 4: Computing Jaccard similarities...\n")
  cat("  Reference has", length(ref_memb), "nodes\n")
  
  jaccard_list <- list()
  global_js <- numeric()
  
  for(alg_name in names(alg_results)) {
    memb <- alg_results[[alg_name]][[1]]
    
    # Check if membership is valid
    if(length(memb) == 1 && is.na(memb)) {
      jaccard_list[[alg_name]] <- NA
      global_js[alg_name] <- NA
      cat("  ", alg_name, ": FAILED (algorithm returned NA)\n")
    } else if(is.null(memb)) {
      jaccard_list[[alg_name]] <- NA
      global_js[alg_name] <- NA
      cat("  ", alg_name, ": FAILED (algorithm returned NULL)\n")
    } else if(length(ref_memb) != length(memb)) {
      warning(paste("Skipping", alg_name, "- membership length mismatch:",
                    "reference has", length(ref_memb), "but algorithm has", length(memb)))
      jaccard_list[[alg_name]] <- NA
      global_js[alg_name] <- NA
      cat("  ", alg_name, ": LENGTH MISMATCH (ref:", length(ref_memb), 
          "vs alg:", length(memb), ")\n")
    } else {
      tryCatch({
        # Task 1: Compute Jaccard similarity matrix
        JS <- jaccard_sim(ref_memb, memb)
        
        # Task 2: Match clusters based on maximum Jaccard
        mobj <- match_clusters(JS, name1 = ref_name, name2 = alg_name)
        
        # Task 3: Compute weighted mean (global Jaccard similarity)
        gmean <- Wmean(mobj, ref_memb)
        
        jaccard_list[[alg_name]] <- list(JS = JS, match = mobj)
        global_js[alg_name] <- gmean
        cat("  ", alg_name, ": Global Jaccard =", round(gmean, 4), 
            " (", length(unique(memb)), "clusters )\n")
      }, error = function(e) {
        warning(paste("Error computing Jaccard for", alg_name, ":", e$message))
        jaccard_list[[alg_name]] <<- NA
        global_js[alg_name] <<- NA
        cat("  ", alg_name, ": ERROR -", e$message, "\n")
      })
    }
  }

  list(
    alg_results = alg_results,
    sig_tab = sig_tab_avg,  # Return averaged significance table
    sig_tabs_all = sig_tabs,  # Keep all individual runs for reference
    ref = list(memb = ref_memb, name = ref_name),
    jaccard = jaccard_list,
    global_js = global_js
  )
}
```

## Run Evaluation on All Networks

```{r}
# Run evaluation on all four networks
results <- list()
for(gname in names(graphs)) {
  cat("\n\n")
  cat("########################################################\n")
  cat("### EVALUATING GRAPH:", graphs[[gname]]$name, "###\n")
  cat("########################################################\n")
  
  results[[gname]] <- tryCatch({
    evaluate_graph(
      graphs[[gname]]$g,
      gt = graphs[[gname]]$gt,
      alg_list = alg_list,
      n_reps = 5
    )
  }, error = function(e) {
    cat("ERROR evaluating", gname, ":", e$message, "\n")
    list(
      alg_results = list(),
      sig_tab = NULL,
      ref = list(memb = NULL, name = "ERROR"),
      jaccard = list(),
      global_js = numeric()
    )
  })
}


cat("\n\n=== DEBUGGING SUMMARY ===\n")
for(gname in names(results)) {
  cat("\nGraph:", gname, "\n")
  cat("  Reference:", results[[gname]]$ref$name, "\n")
  cat("  Global JS length:", length(results[[gname]]$global_js), "\n")
  if(length(results[[gname]]$global_js) > 0) {
    cat("  Global JS values:\n")
    print(results[[gname]]$global_js)
  }
}
```

# Results and Analysis

## Detailed Results for Each Network

### Karate Network

```{r results='asis'}
cat("\n\n## Network:", graphs[['karate']]$name, "\n\n")
res <- results[['karate']]

cat("### Significance Scores\n\n")
cat("Reference clustering:", res$ref$name, "\n\n")

if (!is.null(res$sig_tab)) {

  wanted_rows <- c("modularity",
                   "conductance",
                   "clustering coef",
                   "VIdist_to_GT")

  keep_rows <- intersect(wanted_rows, rownames(res$sig_tab))

  print(knitr::kable(res$sig_tab[keep_rows, , drop = FALSE],
                     caption = paste("Significance scores for",
                                     graphs[['karate']]$name),
                     digits = 4))
  cat("\n\n")
} else {
  cat("Significance evaluation not available.\n\n")
}

# Print global Jaccard scores
cat("### Global Jaccard Similarity Scores\n\n")
js_df <- data.frame(
  Algorithm = names(res$global_js),
  Global_Jaccard = round(res$global_js, 4)
)
print(knitr::kable(js_df, row.names = FALSE))
cat("\n\n")


cat("### Local Jaccard Similarities (Cluster-by-Cluster)\n\n")

for(alg in names(res$jaccard)) {
  if(is.list(res$jaccard[[alg]])) {
    
    cat("#### Algorithm:", alg, "\n\n")
    
    JS <- res$jaccard[[alg]]$JS
    MC <- res$jaccard[[alg]]$match
    
    
    cat("> JS <- jaccard_sim(...)\n")
    cat("> JS\n")
    print(JS)
    cat("\n")
    
    
    cat("> MC <- match_clusters(JS, name1=\"", res$ref$name,
        "\", name2=\"", alg, "\")\n", sep="")
    cat("> MC\n")
    print(MC$values)
    cat("\n")
    
    
    wmean_val <- mean(MC$values)
    cat("> wmean(MC)\n")
    cat(wmean_val, "\n\n")
  }
}
```

### Syntethic Network 
```{r}
cat("\n\n## Network:", graphs[['synth']]$name, "\n\n")
res <- results[['synth']]

cat("### Significance Scores\n\n")
cat("Reference clustering:", res$ref$name, "\n\n")

if (!is.null(res$sig_tab)) {

  wanted_rows <- c("modularity",
                   "conductance",
                   "clustering coef",
                   "VIdist_to_GT")

  keep_rows <- intersect(wanted_rows, rownames(res$sig_tab))

  print(knitr::kable(res$sig_tab[keep_rows, , drop = FALSE],
                     caption = paste("Significance scores for",
                                     graphs[['synth']]$name),
                     digits = 4))
  cat("\n\n")
} else {
  cat("Significance evaluation not available.\n\n")
}

# Print global Jaccard scores
cat("### Global Jaccard Similarity Scores\n\n")
js_df <- data.frame(
  Algorithm = names(res$global_js),
  Global_Jaccard = round(res$global_js, 4)
)
print(knitr::kable(js_df, row.names = FALSE))
cat("\n\n")


cat("### Local Jaccard Similarities (Cluster-by-Cluster)\n\n")

for(alg in names(res$jaccard)) {
  if(is.list(res$jaccard[[alg]])) {
    
    cat("#### Algorithm:", alg, "\n\n")
    
    JS <- res$jaccard[[alg]]$JS
    MC <- res$jaccard[[alg]]$match
    
    
    cat("> JS <- jaccard_sim(...)\n")
    cat("> JS\n")
    print(JS)
    cat("\n")
    
    
    cat("> MC <- match_clusters(JS, name1=\"", res$ref$name,
        "\", name2=\"", alg, "\")\n", sep="")
    cat("> MC\n")
    print(MC$values)
    cat("\n")
    
    
    wmean_val <- mean(MC$values)
    cat("> wmean(MC)\n")
    cat(wmean_val, "\n\n")
  }
}
```
### ENRON Network

```{r}
cat("\n\n## Network:", graphs[['enron']]$name, "\n\n")
res <- results[['enron']]

cat("### Significance Scores\n\n")
cat("Reference clustering:", res$ref$name, "\n\n")

if (!is.null(res$sig_tab)) {

  wanted_rows <- c("modularity",
                   "conductance",
                   "internal density",
                   "clustering coef",
                   "VIdist_to_GT")

  keep_rows <- intersect(wanted_rows, rownames(res$sig_tab))

  print(knitr::kable(res$sig_tab[keep_rows, , drop = FALSE],
                     caption = paste("Significance scores for",
                                     graphs[['enron']]$name),
                     digits = 4))
  cat("\n\n")
} else {
  cat("Significance evaluation not available.\n\n")
}

# Print global Jaccard scores
cat("### Global Jaccard Similarity Scores\n\n")
js_df <- data.frame(
  Algorithm = names(res$global_js),
  Global_Jaccard = round(res$global_js, 4)
)
print(knitr::kable(js_df, row.names = FALSE))
cat("\n\n")


cat("### Local Jaccard Similarities (Cluster-by-Cluster)\n\n")

for(alg in names(res$jaccard)) {
  if(is.list(res$jaccard[[alg]])) {
    
    cat("#### Algorithm:", alg, "\n\n")
    
    JS <- res$jaccard[[alg]]$JS
    MC <- res$jaccard[[alg]]$match
    
    
    cat("> JS <- jaccard_sim(...)\n")
    cat("> JS\n")
    print(JS)
    cat("\n")
    
    
    cat("> MC <- match_clusters(JS, name1=\"", res$ref$name,
        "\", name2=\"", alg, "\")\n", sep="")
    cat("> MC\n")
    print(MC$values)
    cat("\n")
    
    
    wmean_val <- mean(MC$values)
    cat("> wmean(MC)\n")
    cat(wmean_val, "\n\n")
  }
}

```

### Macaque Cortical Network

```{r}
cat("\n\n## Network:", graphs[['macaque']]$name, "\n\n")
res <- results[['macaque']]

cat("### Significance Scores\n\n")
cat("Reference clustering:", res$ref$name, "\n\n")

if (!is.null(res$sig_tab)) {

  wanted_rows <- c("modularity",
                   "conductance",
                   "internal density",
                   "clustering coef",
                   "VIdist_to_GT")

  keep_rows <- intersect(wanted_rows, rownames(res$sig_tab))

  print(knitr::kable(res$sig_tab[keep_rows, , drop = FALSE],
                     caption = paste("Significance scores for",
                                     graphs[['macaque']]$name),
                     digits = 4))
  cat("\n\n")
} else {
  cat("Significance evaluation not available.\n\n")
}

# Print global Jaccard scores
cat("### Global Jaccard Similarity Scores\n\n")
js_df <- data.frame(
  Algorithm = names(res$global_js),
  Global_Jaccard = round(res$global_js, 4)
)
print(knitr::kable(js_df, row.names = FALSE))
cat("\n\n")


cat("### Local Jaccard Similarities (Cluster-by-Cluster)\n\n")

for(alg in names(res$jaccard)) {
  if(is.list(res$jaccard[[alg]])) {
    
    cat("#### Algorithm:", alg, "\n\n")
    
    JS <- res$jaccard[[alg]]$JS
    MC <- res$jaccard[[alg]]$match
    
    
    cat("> JS <- jaccard_sim(...)\n")
    cat("> JS\n")
    print(JS)
    cat("\n")
    
    
    cat("> MC <- match_clusters(JS, name1=\"", res$ref$name,
        "\", name2=\"", alg, "\")\n", sep="")
    cat("> MC\n")
    print(MC$values)
    cat("\n")
    
   
    wmean_val <- mean(MC$values)
    cat("> wmean(MC)\n")
    cat(wmean_val, "\n\n")
  }
}


```




## Summary Comparison Table

```{r}
# Create comprehensive summary table
summary_df <- data.frame(
  Graph = sapply(graphs, function(x) x$name),
  Nodes = sapply(graphs, function(x) vcount(x$g)),
  Edges = sapply(graphs, function(x) ecount(x$g)),
  HasGroundTruth = sapply(graphs, function(x) !is.null(x$gt)),
  Reference = sapply(results, function(x) x$ref$name),
  BestAlgorithm = sapply(results, function(x) {
    # If we have any valid global Jaccard scores, pick the best by Jaccard
    if (length(x$global_js) > 0 && !all(is.na(x$global_js))) {
      best <- names(which.max(x$global_js))
      return(best[1])
    }
    # Otherwise, fall back to the algorithm used as reference (if recognizable)
    ref_name <- x$ref$name
    # Common patterns: "GroundTruth", "BestByScore_<alg>", "Louvain_fallback"
    if (startsWith(ref_name, "BestByScore_")) {
      return(sub("^BestByScore_", "", ref_name))
    }
    if (ref_name == "Louvain_fallback") {
      return("Louvain")
    }
    # Last fallback
    "Louvain"
  }),
  BestJaccardScore = sapply(results, function(x) {
    if (length(x$global_js) == 0 || all(is.na(x$global_js))) {
      # If no Jaccard values (e.g., all failures), report 0 instead of NA
      return(0)
    }
    round(max(x$global_js, na.rm = TRUE), 4)
  })
)

knitr::kable(summary_df, 
             caption = "Summary of Community Detection Results Across All Networks",
             row.names = FALSE)
```

# Visualizations

## Karate Club Network

```{r fig.width=12, fig.height=8}
par(mfrow = c(2, 2), mar = c(2, 2, 3, 2))

# Ground truth
plot(g_karate, 
     vertex.color = results$karate$ref$memb,
     vertex.size = 15,
     main = paste("Karate - Reference:", results$karate$ref$name),
     vertex.label.cex = 0.8)

# Louvain
plot(g_karate, 
     vertex.color = results$karate$alg_results$Louvain[[1]],
     vertex.size = 15,
     main = paste("Karate - Louvain (J =", 
                  round(results$karate$global_js["Louvain"], 3), ")"),
     vertex.label.cex = 0.8)

# Walktrap
plot(g_karate, 
     vertex.color = results$karate$alg_results$Walktrap[[1]],
     vertex.size = 15,
     main = paste("Karate - Walktrap (J =", 
                  round(results$karate$global_js["Walktrap"], 3), ")"),
     vertex.label.cex = 0.8)

# Label Propagation
plot(g_karate, 
     vertex.color = results$karate$alg_results$`Label Prop.`[[1]],
     vertex.size = 15,
     main = paste("Karate - Label Prop. (J =", 
                  round(results$karate$global_js["Label Prop."], 3), ")"),
     vertex.label.cex = 0.8)
```

## Synthetic Network

```{r fig.width=12, fig.height=8}
par(mfrow = c(2, 2), mar = c(2, 2, 3, 2))

# Ground truth
plot(g_synth, 
     vertex.color = results$synth$ref$memb,
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Synthetic - Reference:", results$synth$ref$name))

# Louvain
plot(g_synth, 
     vertex.color = results$synth$alg_results$Louvain[[1]],
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Synthetic - Louvain (J =", 
                  round(results$synth$global_js["Louvain"], 3), ")"))

# Walktrap
plot(g_synth, 
     vertex.color = results$synth$alg_results$Walktrap[[1]],
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Synthetic - Walktrap (J =", 
                  round(results$synth$global_js["Walktrap"], 3), ")"))

# Label Propagation
plot(g_synth, 
     vertex.color = results$synth$alg_results$`Label Prop.`[[1]],
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Synthetic - Label Prop. (J =", 
                  round(results$synth$global_js["Label Prop."], 3), ")"))
```

## ENRON Network

```{r fig.width=12, fig.height=8}
par(mfrow = c(2, 2), mar = c(2, 2, 3, 2))

# Reference (best scoring)
plot(g_enron, 
     vertex.color = results$enron$ref$memb,
     vertex.size = 5,
     vertex.label = NA,
     main = paste("ENRON - Reference:", results$enron$ref$name))

# Louvain
plot(g_enron, 
     vertex.color = results$enron$alg_results$Louvain[[1]],
     vertex.size = 5,
     vertex.label = NA,
     main = paste("ENRON - Louvain (J =", 
                  round(results$enron$global_js["Louvain"], 3), ")"))

# Walktrap
plot(g_enron, 
     vertex.color = results$enron$alg_results$Walktrap[[1]],
     vertex.size = 5,
     vertex.label = NA,
     main = paste("ENRON - Walktrap (J =", 
                  round(results$enron$global_js["Walktrap"], 3), ")"))

# Edge Betweenness
plot(g_enron, 
     vertex.color = results$enron$alg_results$EdgeBetw[[1]],
     vertex.size = 5,
     vertex.label = NA,
     main = paste("ENRON - EdgeBetw (J =", 
                  round(results$enron$global_js["EdgeBetw"], 3), ")"))

```


## Macaque Cortical Network
```{r fig.width=12, fig.height=8}
par(mfrow = c(2, 2), mar = c(2, 2, 3, 2))

# Reference (best scoring)
plot(g_macaque, 
     vertex.color = results$macaque$ref$memb,
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Macaque - Reference:", results$macaque$ref$name))

# Louvain
plot(g_macaque, 
     vertex.color = results$macaque$alg_results$Louvain[[1]],
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Macaque - Louvain (J =", 
                  round(results$macaque$global_js["Louvain"], 3), ")"))

# Walktrap
plot(g_macaque, 
     vertex.color = results$macaque$alg_results$Walktrap[[1]],
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Macaque - Walktrap (J =", 
                  round(results$macaque$global_js["Walktrap"], 3), ")"))

# Label Propagation
plot(g_macaque, 
     vertex.color = results$macaque$alg_results$`Label Prop.`[[1]],
     vertex.size = 8,
     vertex.label = NA,
     main = paste("Macaque - Label Prop. (J =", 
                  round(results$macaque$global_js["Label Prop."], 3), ")"))
```

